---
title: "WIP MADC Data Unification"
author: "Nicolas May"
date: "1/7/2019"
output: 
  html_document:
    theme: cerulean
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Requirements

## Load Useful Libraries

```{r}
# USEFUL LIBRARIES ----
library(dplyr)
library(stringr)
library(knitr)
library(kableExtra)
```

## Load Useful Variables

```{r}
# USEFUL VARS ----
`%>%` <- `%>%`
source('~/Desktop/config.R')
rm(BOX_CLIENT_ID); rm(BOX_CLIENT_SECRET); rm(BOX_REDIRECT_URI)
rm(REDCAP_DATA_REQUESTS_TOKEN)

## switch to access API (TRUE) or not (FALSE)
get_api_data <- TRUE
```

## Load Useful Helper Functions

```{r}
# USEFUL HELPER FUNCTIONS ----
remove_NAs <- function(x) {
  if (is.vector(x)) return(x[!is.na(x)])
  else stop('x is not a vector')
}
```


# Get Data

## Get REDCap Project Data Fields

### UDS 2
```{r}
# _ UDS 2 ----
if (get_api_data) {
  export_fields_u2_json <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS2,
    content='exportFieldNames',
    format='json',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
export_fields_u2_df <- jsonlite::fromJSON(export_fields_u2_json) %>% 
  na_if('')
head(export_fields_u2_df) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

### UDS 3 Old
```{r}
# _ UDS 3 (old) ----
if (get_api_data) {
  export_fields_u31_json <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS31,
    content='exportFieldNames',
    format='json',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
export_fields_u31_df <- jsonlite::fromJSON(export_fields_u31_json) %>% 
  na_if('')
head(export_fields_u31_df) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

### UDS 3 New
```{r}
# _ UDS 3 (new) ----
if (get_api_data) {
  export_fields_u32_json <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS3,
    content='exportFieldNames',
    format='json',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
export_fields_u32_df <- jsonlite::fromJSON(export_fields_u32_json) %>% 
  na_if('')
head(export_fields_u32_df) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

### MiNDSet Registry
```{r}
# _ MiNDSet ----
if (get_api_data) {
  export_fields_ms_json <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_MINDSET,
    content='exportFieldNames',
    format='json',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
export_fields_ms_df <- jsonlite::fromJSON(export_fields_ms_json) %>% 
  na_if('')
head(export_fields_ms_df) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

## Get Human-Resolved Fields 

Because there are asystematic mismatches between the three UDS datsets that MADC has stored in REDCap, there are two XLSX files that require human creation/maintenance. Loading and processing the data in the files makes it possible to resolve field name mismatches in order to harmonize and unify the data.

```{r}
# _ Get work-in-progress translation dictionary ----
trans_dict <- readxl::read_excel('WIP__translation_dictionary.xlsx')
head(trans_dict) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)

# _ Get work-in-progress UDS3 ivp-fvp-tvp matches ----
u32_ift_match <- readxl::read_excel('WIP__uds3_ift_matches.xlsx') %>% 
  select(field_ivp, form_ivp, 
         field_fvp, form_fvp,
         field_tvp, form_tvp)
head(u32_ift_match) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

## Process Dataset Fields

### UDS 2
```{r}
# _ UDS 2 ----
fields_u2_raw <- trans_dict$field_u2
fields_u2_raw <- remove_NAs(fields_u2_raw)
fields_u2 <- fields_u2_raw %>% paste(collapse = ',')
```

### UDS 3 Old
```{r}
# _ UDS 3 (old) ----
fields_u31_raw <- trans_dict$field_u31
fields_u31_raw <- remove_NAs(fields_u31_raw)
fields_u31 <- fields_u31_raw %>% paste(collapse = ',')
```

### UDS 3 New

The fields for UDS 3 (New) require a little more work because there are three packets to collect participant data:

1. initial visit, IVP
2. follow-up visit, FVP
3. telephone visit, TVP

```{r}
# _ UDS 3 (new) ----
# _ _ IVP
fields_u32_raw_i <- trans_dict$field_u32
# _ _ FVP
fields_u32_raw_fu <- u32_ift_match %>% 
  filter(field_ivp %in% fields_u32_raw_i) %>% 
  filter(!is.na(field_fvp)) %>% 
  pull(field_fvp)
# _ _ TVP
fields_u32_raw_tele <- u32_ift_match %>% 
  filter(field_ivp %in% fields_u32_raw_i) %>% 
  filter(!is.na(field_tvp)) %>%
  pull(field_tvp)
# _ _ IVP + FVP + TVP
fields_u32_raw <- c(fields_u32_raw_i
                    , fields_u32_raw_fu
                    , fields_u32_raw_tele)
fields_u32_raw <- remove_NAs(fields_u32_raw) # remove NAs
fields_u32 <- fields_u32_raw %>% paste(collapse = ',') 
```

## REDCap API Data Retrieval

### UDS 2
```{r}
# _ UDS 2 ----
if (get_api_data) {
  json_u2 <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS2,
    content='record',
    format='json',
    type='flat',
    fields=fields_u2,
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
df_u2 <- jsonlite::fromJSON(json_u2) %>% na_if('')
# Clean out '___1' from field some field names -- May need to generalize later
names(df_u2) <- str_replace(names(df_u2), 
                            pattern = "___1", 
                            replacement = "")
```

### UDS 3 Old
```{r}
# _ UDS 3 (old) ----
if (get_api_data) {
  json_u31 <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS31,
    content='record',
    format='json',
    type='flat',
    fields=fields_u31,
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
df_u31 <- jsonlite::fromJSON(json_u31) %>% na_if('')
```

### UDS 3 New
```{r}
# _ UDS 3 (new) ----
if (get_api_data) {
  json_u32 <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS3,
    content='record',
    format='json',
    type='flat',
    fields=fields_u32,
    rawOrLabel='raw',
    rawOrLabelHeaders='raw',
    exportCheckboxLabel='false',
    exportSurveyFields='false',
    exportDataAccessGroups='false',
    returnFormat='json'#,
    # .opts = list(ssl.verifypeer = FALSE) # using linux
  )
}
df_u32 <- jsonlite::fromJSON(json_u32) %>% na_if('')
```

## Write Raw Data To CSV

This comes in handy when diagnosising and resolving possible code errors.

```{r}
readr::write_csv(df_u2, './Raw Data/df_u2.csv', na = '')
readr::write_csv(df_u31, './Raw Data/df_u31.csv', na = '')
readr::write_csv(df_u32, './Raw Data/df_u32.csv', na = '')
```


# Restructure Data

Since the UDS 3 (New) strcuture will be the standard template for all unified MADC UDS data, both UDS 2 and UDS 3 (Old) need to be restructured to match the structure of UDS 3 (New), viz., the IVP/FVP/TVP format.

## UDS 3 (New) Data Structure As Standard

### UDS 2
```{r}
# IVP/FVP/TVP TRANSFORM (UDS 2, UDS 3 old) ----

# _ UDS 2 ----
# _ _ UDS 2 IVP ----
df_u2_i <- df_u2 %>% 
  filter(a1pkt_type == 'I')
# _ _ UDS 2 FVP ----
u32_fvp_vars <- str_replace(fields_u32_raw_fu, '^fu_|^fu', '')
u2_fvp_vars <- trans_dict %>% 
  filter(field_u32 %in% u32_fvp_vars) %>% 
  pull(field_u2) %>% 
  remove_NAs(.)
df_u2_f <- df_u2 %>%
  filter(a1pkt_type == 'F') %>%
  rename_at(.vars = vars(one_of(u2_fvp_vars)),
            .funs = funs(str_replace(., '(.*)', 'fu_\\1')))
# _ _ UDS 2 TVP ----
u32_tvp_vars <- str_replace(fields_u32_raw_tele, 'tele_', '')
u2_tvp_vars <- trans_dict %>% 
  filter(field_u32 %in% u32_tvp_vars) %>% 
  pull(field_u2) %>% 
  remove_NAs(.)
df_u2_t <- df_u2 %>% 
  filter(a1pkt_type == 'T') %>% 
  rename_at(.vars = vars(one_of(u2_tvp_vars)),
            .funs = funs(str_replace(., '(.*)', 'tele_\\1')))
# _ _ Row bind UDS 2 I+F+T ----
df_u2_ift <- bind_rows(df_u2_i, df_u2_f, df_u2_t)
```

### UDS 3 (Old)
```{r}
# IVP/FVP/TVP TRANSFORM (UDS 2, UDS 3 old) ----

# _ UDS 3 (old) ----
# _ _ UDS 3 (old) IVP ----
df_u31_i <- df_u31 %>% 
  filter(a1pkt_type == 'I')
# _ _ UDS 3 (old) FVP ----
u32_fvp_vars <- str_replace(fields_u32_raw_fu, 'fu_', '')
u31_fvp_vars <- trans_dict %>% 
  filter(field_u32 %in% u32_fvp_vars) %>% 
  pull(field_u31) %>% 
  remove_NAs(.)
df_u31_f <- df_u31 %>% 
  filter(a1pkt_type == 'F') %>% 
  rename_at(.vars = vars(one_of(u31_fvp_vars)),
            .funs = funs(str_replace(., '(.*)', 'fu_')))
# _ _ UDS 3 (old) TVP ----
u32_tvp_vars <- str_replace(fields_u32_raw_tele, 'tele_', '')
u31_tvp_vars <- trans_dict %>% 
  filter(field_u32 %in% u32_tvp_vars) %>% 
  pull(field_u31) %>% 
  remove_NAs(.)
df_u31_t <- df_u31 %>% 
  filter(a1pkt_type == 'T') %>% 
  rename_at(.vars = vars(one_of(u31_tvp_vars)),
            .funs = funs(str_replace(., '(.*)', 'tele_')))
# _ _ Row bind UDS 3 (old) I+F+T ----
df_u31_ift <- bind_rows(df_u31_i, df_u31_f, df_u31_t)
```

# Stitch Data Together

Based on the translation dictionary (`WIP__translation_diction.xlsx`), we'll stitch together all the UDS data into one harmonized dataset.

## Build Standard Names DF (`std_names_df`)

### Set up the empty df

```{r}
# _ Build standard names df ----
## Set up empty df
std_names_df <- data.frame(matrix(data = NA_character_,
                                  nrow = 0,
                                  ncol = 2),
                           stringsAsFactors = FALSE)
names(std_names_df) <- c('std_source', 'std_field')
head(std_names_df) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

### Loop through rows of `trans_dict` to standardize field names

`trans_dict` is just a df of the spreadsheet `WIP__translation_dictionary.xlsx`. From this, we'll grab first the UDS 3 New field name; if that doesn't exist, we'll grab the UDS 3 Old field name; if that doesn't exist, it'll be the UDS 2 field name.

From this process is born the standard translation dictionary, `trans_dict_std`.

```{r}
## Loop through rows of `trans_dict`
for (i in seq_len(nrow(trans_dict))) {
  
  ## Std field name is from UDS 3 (new), then UDS 3 (old), then UDS 2
  if (!is.na(trans_dict[i, 'field_u32'])) {
    std_names_df[i, ] <- list('field_u32', trans_dict[[i, 'field_u32']])
  } else if (!is.na(trans_dict[i, 'field_u31'])) {
    std_names_df[i, ] <- list('field_u31', trans_dict[[i, 'field_u31']])
  } else if (!is.na(trans_dict[i, 'field_u2'])) {
    std_names_df[i, ] <- list('field_u2', trans_dict[[i, 'field_u2']])
  }
  
}
trans_dict_std <- cbind(trans_dict, std_names_df)
head(trans_dict_std) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

### Append `fu_*` and `tele_*` fields to bottom of Standard Translation Dictionary

This chunk uses data from human-created/-maintained `WIP__uds3_ift_matches.xlsx` to append `fu_*` and `tele_*` fields to the bottom of the Standard Translation Dictionary (which started out as human-created/-maintained `WIP__translation_dictionary.xlsx`).

```{r}
## Append `fu_*` fields ----
u32_ift_match_f <- u32_ift_match %>%
  filter(!is.na(field_fvp)) %>%
  filter(field_ivp %in% u32_fvp_vars) %>%
  pull(field_ivp)
for (i in seq_along(u32_ift_match_f)) {
  # cat(paste(i, u32_ift_match_f[i], '\n'))
  # cat(paste(i, nrow(trans_dict_std)+i, '\n'))
  curr_row <- nrow(trans_dict_std) + 1
  ## Add `fu_*` field from within trans_dict_std to end of trans_dict_std
  ## UDS 2
  trans_dict_std[curr_row, 'field_u2'] <-
    paste0('fu_',
           trans_dict_std[[
             which(trans_dict_std$field_u32 == u32_ift_match_f[i]), 'field_u2'
             ]])
  # UDS 3 (old)
  trans_dict_std[curr_row, 'field_u31'] <-
    paste0('fu_',
           trans_dict_std[[
             which(trans_dict_std$field_u32 == u32_ift_match_f[i]), 'field_u31'
             ]])
  # UDS 3 (new)
  trans_dict_std[curr_row, 'field_u32'] <-
    paste0('fu_',
           trans_dict_std[[
             which(trans_dict_std$field_u32 == u32_ift_match_f[i]), 'field_u32'
             ]])
  trans_dict_std[curr_row, 'form_u32'] <-
    str_replace(
      trans_dict_std[[
        which(trans_dict_std$field_u32 == u32_ift_match_f[i]), 'form_u32'
        ]],
      pattern = 'ivp_',
      replacement = 'fvp_')
  trans_dict_std[curr_row, 'Notes'] <-
    '__ synthetic field in UDS 2, UDS 3 (old) __'
  trans_dict_std[curr_row, 'std_source'] <- 'field_u32'
  trans_dict_std[curr_row, 'std_field'] <-
    trans_dict_std[[curr_row, 'field_u32']]
}
tail(trans_dict_std) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

```{r}
## Append `tele_*` fields ----
u32_ift_match_t <- u32_ift_match %>%
  filter(!is.na(field_tvp)) %>%
  filter(field_ivp %in% u32_tvp_vars) %>%
  pull(field_ivp)
for (i in seq_along(u32_ift_match_t)) {
  # cat(paste(i, u32_ift_match_t[i], '\n'))
  # cat(paste(i, nrow(trans_dict_std)+i, '\n'))
  curr_row <- nrow(trans_dict_std) + 1
  ## Add `tele_*` field from within trans_dict_std to end of trans_dict_std
  ## UDS 2
  trans_dict_std[curr_row, 'field_u2'] <-
    paste0('tele_',
           trans_dict_std[[
             which(trans_dict_std$field_u32 == u32_ift_match_t[i]), 'field_u2'
             ]])
  # UDS 3 (old)
  trans_dict_std[curr_row, 'field_u31'] <-
    paste0('tele_',
           trans_dict_std[[
             which(trans_dict_std$field_u32 == u32_ift_match_t[i]), 'field_u31'
             ]])
  # UDS 3 (new)
  trans_dict_std[curr_row, 'field_u32'] <-
    paste0('tele_',
           trans_dict_std[[
             which(trans_dict_std$field_u32 == u32_ift_match_t[i]), 'field_u32'
             ]])
  trans_dict_std[curr_row, 'form_u32'] <-
    str_replace(
      trans_dict_std[[
        which(trans_dict_std$field_u32 == u32_ift_match_t[i]), 'form_u32'
        ]],
      pattern = 'ivp_',
      replacement = 'tvp_')
  trans_dict_std[curr_row, 'Notes'] <-
    '__ synthetic field in UDS 2, UDS 3 (old) __'
  trans_dict_std[curr_row, 'std_source'] <- 'field_u32'
  trans_dict_std[curr_row, 'std_field'] <-
    trans_dict_std[[curr_row, 'field_u32']]
}
tail(trans_dict_std) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

Now remove any instances of non-existing field names after `fu_*` and `tele_*` preprends.

```{r}
# _ Remove any instances of 'fu_NA', 'tele_NA', 'fu_', 'tele_' -----
trans_dict_std <- trans_dict_std %>% na_if('fu_NA')
trans_dict_std <- trans_dict_std %>% na_if('tele_NA')
trans_dict_std <- trans_dict_std %>% na_if('fu_')
trans_dict_std <- trans_dict_std %>% na_if('tele_')
tail(trans_dict_std) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

## Build Stitched DF (`df_u2_u31_u32`)

### Create empty df

```{r}
# _ Build stitched data df ----
## Stitched df is `df_u2_u31_u32`
df_u2_u31_u32 <- data.frame(matrix(data = NA_character_,
                                   nrow = sum(nrow(df_u2_ift),
                                              nrow(df_u31_ift),
                                              nrow(df_u32)),
                                   ncol = nrow(trans_dict_std)))
names(df_u2_u31_u32) <- trans_dict_std$std_field
```

### Build `df_u2_u31_u32`

To accomplish this, we iterate over the rows of `trans_dict_std` and build `df_u2_u31_u32` column by column.

```{r}
# Loop through `trans_dict_std` rows to build stitched df column by column
## ... using df_u2_ift, df_u31_ift, df_u32
cat("Number of columns in df_u2_u31_u32 df:\n")
for (i in seq_len(nrow(trans_dict_std))) {
  # for (i in 1:601) {
  cat(paste(i, ' '))
  
  ## Build temp UDS 2 vector
  if (!is.na(trans_dict_std[i, 'field_u2']) &&
      !is.null(df_u2_ift[[trans_dict_std[i, 'field_u2']]])) {
    temp_u2_vec <- df_u2_ift[[trans_dict_std[i, 'field_u2']]]
  } else {
    temp_u2_vec <- rep(NA_character_, times = nrow(df_u2_ift))
  }
  
  ## Build temp UDS 3 (old) vector
  if (!is.na(trans_dict_std[i, 'field_u31']) &&
      !is.null(df_u31_ift[[trans_dict_std[i, 'field_u31']]])) {
    temp_u31_vec <- df_u31_ift[[trans_dict_std[i, 'field_u31']]]
  } else {
    temp_u31_vec <- rep(NA_character_, times = nrow(df_u31_ift))
  }
  
  ## Build temp UDS 3 (new) vector
  if (!is.na(trans_dict_std[i, 'field_u32']) &&
      !is.null(df_u32[[trans_dict_std[i, 'field_u32']]])) {
    temp_u32_vec <- df_u32[[trans_dict_std[i, 'field_u32']]]
  } else {
    temp_u32_vec <- rep(NA_character_, times = nrow(df_u32))
  }
  
  ## Concat `temp_*_vec` vectors
  temp_u2_u31_u32_vec <- c(temp_u2_vec, temp_u31_vec, temp_u32_vec)
  # print(length(temp_u2_u31_u32_vec))
  
  ## Lay concat'd `temp_*_vec` vectors into stitched df column
  df_u2_u31_u32[, i] <- temp_u2_u31_u32_vec
}
```

### Reduce the size of `df_u2_u31_u32` by guessing column data types

```{r}
print(object.size(df_u2_u31_u32), units = 'auto')
# _ Guess column types
df_u2_u31_u32 <- suppressMessages( readr::type_convert(df_u2_u31_u32) )
print(object.size(df_u2_u31_u32), units = 'auto')
```

## Write Harmonized Data To CSV

Write the resulting harmonized dataset `df_u2_u31_u32` to a CSV file of the same name.

```{r}
# WRITE TO CSV ----
readr::write_csv(df_u2_u31_u32, 'df_u2_u31_u32.csv', na = '')
```


# Build Data Dictionary

## Get UDS Fields

### UDS 2
```{r}
# UDS 2
data_dict_fields_u2_raw <- trans_dict_std %>% 
  select(std_source, std_field) %>% 
  filter(std_source == 'field_u2') %>% 
  pull(std_field)
```

### UDS 3 Old
```{r}
# UDS 3 (Old)
data_dict_fields_u31_raw <- trans_dict_std %>% 
  select(std_source, std_field) %>% 
  filter(std_source == 'field_u31') %>% 
  pull(std_field)
```

### UDS 3 New
```{r}
# UDS 3 (New)
data_dict_fields_u32_raw <- trans_dict_std %>% 
  select(std_source, std_field) %>% 
  filter(std_source == 'field_u32') %>% 
  pull(std_field)
```

## Retrieve Data Dictionary via REDCap API

### UDS 2
```{r}
json_data_dict_u2 <- RCurl::postForm(
  uri=REDCAP_API_URI,
  token=REDCAP_API_TOKEN_UDS2,
  content='metadata',
  format='json',
  returnFormat='json'
)
df_data_dict_u2_all <- jsonlite::fromJSON(json_data_dict_u2)
df_data_dict_u2 <- df_data_dict_u2_all %>% 
  filter(field_name %in% data_dict_fields_u2_raw)
```

### UDS 3 (Old)
```{r}
json_data_dict_u31 <- RCurl::postForm(
  uri=REDCAP_API_URI,
  token=REDCAP_API_TOKEN_UDS31,
  content='metadata',
  format='json',
  returnFormat='json'
)
df_data_dict_u31_all <- jsonlite::fromJSON(json_data_dict_u31)
df_data_dict_u31 <- df_data_dict_u31_all %>% 
  filter(field_name %in% data_dict_fields_u31_raw)
```

### UDS 3 (New)
```{r}
json_data_dict_u32 <- RCurl::postForm(
  uri=REDCAP_API_URI,
  token=REDCAP_API_TOKEN_UDS3,
  content='metadata',
  format='json',
  returnFormat='json'
)
df_data_dict_u32_all <- jsonlite::fromJSON(json_data_dict_u32)
df_data_dict_u32 <- df_data_dict_u31_all %>% 
  filter(field_name %in% data_dict_fields_u32_raw)
```

## Rowbind Data Dictionaries & Order

Order by form name, then field name.

```{r}
df_data_dict <- bind_rows(df_data_dict_u2,
                          df_data_dict_u31,
                          df_data_dict_u32)
df_data_dict_form <- df_data_dict %>% 
  arrange(form_name, field_name)
df_data_dict_field <- df_data_dict %>% 
  arrange(field_name)

head(df_data_dict_field) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)

head(df_data_dict_form) %>% 
  kable() %>% 
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
    font_size = 9)
```

## Write Harmonized Data Dictionary To CSV

```{r}
readr::write_csv(df_data_dict_form, 'df_data_dict_form.csv', na = '')
readr::write_csv(df_data_dict_field, 'df_data_dict_field.csv', na = '')
```


```
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
