---
title: "WIP MADC Data Unification"
author: "Nicolas May"
date: "1/7/2019"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: sandstone
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Requirements

## Load Useful Libraries

```{r load_libs}
# USEFUL LIBRARIES ----
suppressMessages( library(dplyr) )
suppressMessages( library(readr) )
suppressMessages( library(stringr) )
```

## Load Useful Variables

```{r}
# USEFUL VARS ----
source("~/Box/Documents/R_helpers/config.R")
rm(BOX_CLIENT_ID); rm(BOX_CLIENT_SECRET); rm(BOX_REDIRECT_URI)
rm(REDCAP_DATA_REQUESTS_TOKEN)
source("~/Box/Documents/R_helpers/helpers.R")

## switch to access API (TRUE) or not (FALSE)
GET_API_DATA <- TRUE
```

## Load Useful Helper Functions

```{r}
# USEFUL HELPER FUNCTIONS ----

remove_NAs <- function(x) {
  if (!is.vector(x)) { stop("x is not a vector") }
  x[!is.na(x)]
}

pretty_print_df <- function(df) {
  df %>% 
    knitr::kable() %>%
    kableExtra::kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "responsive"),
      font_size = 9)
}
```


# Get Data

## Get REDCap Project Data Fields

### UDS 2
```{r dl_uds2_data_fields}
# _ UDS 2 ----
if (GET_API_DATA) {
  export_fields_u2_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_UDS2,
      content="exportFieldNames",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    )
}
export_fields_u2_df <- jsonlite::fromJSON(export_fields_u2_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(export_fields_u2_df, 
                 "Export Fields/export_fields_u2_df.csv", na = "")
head(export_fields_u2_df) # %>% pretty_print_df()
```

### UDS 3 Archive
```{r dl_uds3_archive_data_fields}
# _ UDS 3 (Archive) ----
if (GET_API_DATA) {
  export_fields_u3a_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_UDS3a,
      content="exportFieldNames",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    )
}
export_fields_u3a_df <- jsonlite::fromJSON(export_fields_u3a_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(export_fields_u3a_df, 
                 "Export Fields/export_fields_u3a_df.csv", na = "")
head(export_fields_u3a_df) # %>% pretty_print_df()
```

### UDS 3 New
```{r dl_uds3_new_data_fields}
# _ UDS 3 (New) ----
if (GET_API_DATA) {
  export_fields_u3n_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_UDS3n,
      content="exportFieldNames",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    )
}
export_fields_u3n_df <- jsonlite::fromJSON(export_fields_u3n_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(export_fields_u3n_df, 
                 "Export Fields/export_fields_u3n_df.csv", na = "")
head(export_fields_u3n_df) # %>% pretty_print_df()
```

### MiNDSet Registry
```{r dl_mindset_data_fields}
# _ MiNDSet ----
if (GET_API_DATA) {
  export_fields_ms_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_MINDSET,
      content="exportFieldNames",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    )
}
export_fields_ms_df <- jsonlite::fromJSON(export_fields_ms_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(export_fields_ms_df,
                 "Export Fields/export_fields_ms_df.csv", na = "")
head(export_fields_ms_df) # %>% pretty_print_df()
```


## Get REDCap Project Data Dictionaries

### UDS 2
```{r dl_uds2_data_dict}
# _ UDS 2 ----
if (GET_API_DATA) {
  data_dict_u2_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_UDS2,
      content="metadata",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
data_dict_u2_df <- jsonlite::fromJSON(data_dict_u2_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(data_dict_u2_df, 
                 "Data Dictionaries/data_dict_u2_df.csv", na = "")
head(data_dict_u2_df) # %>% pretty_print_df()
```

### UDS 3 Archive
```{r dl_uds3_archive_data_dict}
# _ UDS 3 (Archive) ----
if (GET_API_DATA) {
  data_dict_u3a_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_UDS3a,
      content="metadata",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
data_dict_u3a_df <- jsonlite::fromJSON(data_dict_u3a_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(data_dict_u3a_df, 
                 "Data Dictionaries/data_dict_u3a_df.csv", na = "")
head(data_dict_u3a_df) # %>% pretty_print_df()
```

### UDS 3 New
```{r dl_uds3_new_data_dict}
# _ UDS 3 (New) ----
if (GET_API_DATA) {
  data_dict_u3n_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_UDS3n,
      content="metadata",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
data_dict_u3n_df <- jsonlite::fromJSON(data_dict_u3n_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(data_dict_u3n_df, 
                 "Data Dictionaries/data_dict_u3n_df.csv", na = "")
head(data_dict_u3n_df) # %>% pretty_print_df()
```

### MiNDSet Registry
```{r dl_mindset_data_dict}
# _ UDS 3 (Archive) ----
if (GET_API_DATA) {
  data_dict_ms_json <- 
    RCurl::postForm(
      uri=REDCAP_API_URI,
      token=REDCAP_API_TOKEN_MINDSET,
      content="metadata",
      format="json",
      returnFormat="json",
      .opts = list(ssl.verifypeer = TRUE) # using linux
    ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
data_dict_ms_df <- jsonlite::fromJSON(data_dict_ms_json) %>% 
  as_tibble() %>% 
  na_if("")
readr::write_csv(data_dict_ms_df, 
                 "Data Dictionaries/data_dict_ms_df.csv", na = "")
head(data_dict_ms_df) # %>% pretty_print_df()
```


## Get Human-Resolved Fields 

Because there are asystematic mismatches between the three UDS datsets that MADC
has stored in REDCap, there are two XLSX files that require human 
creation/maintenance. Loading and processing the data in the files makes it 
possible to resolve field name mismatches in order to harmonize and unify the 
data.

```{r}
# _ Get work-in-progress translation dictionary ----
trans_dict <- readxl::read_excel("WIP__translation_dictionary.xlsx")
head(trans_dict) # %>% pretty_print_df()

# _ Get work-in-progress UDS3 ivp-fvp-tvp matches ----
u3n_ift_match <- readxl::read_excel("WIP__uds3_ift_matches.xlsx") %>% 
  select(field_ivp, form_ivp, 
         field_fvp, form_fvp,
         field_tvp, form_tvp)
head(u3n_ift_match) # %>% pretty_print_df()
```


## Process Dataset Fields

### UDS 2
```{r}
# _ UDS 2 ----
fields_u2_raw <- trans_dict$field_u2
fields_u2_raw <- remove_NAs(fields_u2_raw)
fields_u2 <- fields_u2_raw %>% paste(collapse = ",")
```

### UDS 3 Archive
```{r}
# _ UDS 3 (Archive) ----
fields_u3a_raw <- trans_dict$field_u3a
fields_u3a_raw <- remove_NAs(fields_u3a_raw)
fields_u3a <- fields_u3a_raw %>% paste(collapse = ",")
```

### UDS 3 New

The fields for UDS 3 (New) require a little more work because there are three 
packets to collect participant data:

1. initial visit, IVP
2. follow-up visit, FVP
3. telephone visit, TVP

```{r}
# _ UDS 3 (New) ----
# _ _ IVP
fields_u3n_raw_i <- trans_dict$field_u3n
# _ _ FVP
fields_u3n_raw_fu <- u3n_ift_match %>% 
  filter(field_ivp %in% fields_u3n_raw_i) %>% 
  filter(!is.na(field_fvp)) %>% 
  pull(field_fvp)
# _ _ TVP
fields_u3n_raw_tele <- u3n_ift_match %>% 
  filter(field_ivp %in% fields_u3n_raw_i) %>% 
  filter(!is.na(field_tvp)) %>%
  pull(field_tvp)
# _ _ IVP + FVP + TVP
fields_u3n_raw <- c(fields_u3n_raw_i
                    , fields_u3n_raw_fu
                    , fields_u3n_raw_tele)
fields_u3n_raw <- remove_NAs(fields_u3n_raw) # remove NAs
fields_u3n <- fields_u3n_raw %>% paste(collapse = ",") 
```

## REDCap API Data Retrieval

### UDS 2
```{r dl_uds2_data}
# _ UDS 2 ----
if (GET_API_DATA) {
  json_u2 <- export_redcap_records(uri    = REDCAP_API_URI,
                                   token  = REDCAP_API_TOKEN_UDS2,
                                   fields = fields_u2)
}
df_u2 <- jsonlite::fromJSON(json_u2) %>% 
  as_tibble() %>% 
  na_if("")
# # Clean out "___1" from field some field names -- Generalize later
# names(df_u2) <- str_replace(names(df_u2), 
#                             pattern = "___1", 
#                             replacement = "")
```

### UDS 3 Archive
```{r dl_uds3_archive_data}
# _ UDS 3 (Archive) ----
if (GET_API_DATA) {
  json_u3a <- export_redcap_records(uri    = REDCAP_API_URI,
                                    token  = REDCAP_API_TOKEN_UDS3a,
                                    fields = fields_u3a)
}
df_u3a <- jsonlite::fromJSON(json_u3a) %>% 
  as_tibble() %>% 
  na_if("")
```

### UDS 3 New
```{r dl_uds3_new_data}
# _ UDS 3 (New) ----
if (GET_API_DATA) {
  json_u3n <- export_redcap_records(uri   = REDCAP_API_URI,
                                    token = REDCAP_API_TOKEN_UDS3n)
}
df_u3n <- jsonlite::fromJSON(json_u3n) %>% 
  as_tibble() %>% 
  na_if("")

# Clean out Double Data Entry (DDE) records ending in "--1" or "--2"
df_u3n <- df_u3n %>% 
  # filter(!(str_detect(ptid, "--1$|--2$")))
  filter(str_detect(ptid, "^UM\\d{8}$"))
```

## Write Raw Data To CSV

This comes in handy when diagnosising and resolving possible code errors.

```{r}
readr::write_csv(df_u2,  "./Raw Data/df_u2.csv",  na = "")
readr::write_csv(df_u3a, "./Raw Data/df_u3a.csv", na = "")
readr::write_csv(df_u3n, "./Raw Data/df_u3n.csv", na = "")
```


# Restructure Data

Since the UDS 3 (New) strcuture will be the standard template for all unified 
MADC UDS data, both UDS 2 and UDS 3 (Archive) need to be restructured to match 
the structure of UDS 3 (New), viz., the IVP/FVP/TVP format.

## UDS 3 (New) Data Structure As Standard

### UDS 2
```{r}
# IVP/FVP/TVP TRANSFORM (UDS 2, UDS 3 Archive) ----

# _ UDS 2 ----
# _ _ UDS 2 IVP ----
df_u2_i <- df_u2 %>% 
  filter(a1pkt_type == "I")
# _ _ UDS 2 FVP ----
u3n_fvp_vars <- str_replace(fields_u3n_raw_fu, "^fu_|^fu", "")
u2_fvp_vars <- trans_dict %>% 
  filter(field_u3n %in% u3n_fvp_vars) %>% 
  pull(field_u2) %>% 
  remove_NAs(.)
df_u2_f <- df_u2 %>%
  filter(a1pkt_type == "F") %>%
  rename_at(.vars = vars(one_of(u2_fvp_vars)),
            # .funs = funs(str_replace(., "(.*)", "fu_\\1")))
            .funs = list(~str_replace(., "(.*)", "fu_\\1")))
# _ _ UDS 2 TVP ----
u3n_tvp_vars <- str_replace(fields_u3n_raw_tele, "tele_", "")
u2_tvp_vars <- trans_dict %>% 
  filter(field_u3n %in% u3n_tvp_vars) %>% 
  pull(field_u2) %>% 
  remove_NAs(.)
df_u2_t <- df_u2 %>% 
  filter(a1pkt_type == "T") %>% 
  rename_at(.vars = vars(one_of(u2_tvp_vars)),
            # .funs = funs(str_replace(., "(.*)", "tele_\\1")))
            .funs = list(~str_replace(., "(.*)", "tele_\\1")))
# _ _ Row bind UDS 2 I+F+T ----
df_u2_ift <- bind_rows(df_u2_i, df_u2_f, df_u2_t)
```

### UDS 3 (Archive)
```{r}
# IVP/FVP/TVP TRANSFORM (UDS 2, UDS 3 Archive) ----

# _ UDS 3 (Archive) ----
# _ _ UDS 3 (Archive) IVP ----
df_u3a_i <- df_u3a %>% 
  filter(a1pkt_type == "I")
# _ _ UDS 3 (Archive) FVP ----
u3n_fvp_vars <- str_replace(fields_u3n_raw_fu, "fu_", "")
u3a_fvp_vars <- trans_dict %>% 
  filter(field_u3n %in% u3n_fvp_vars) %>% 
  pull(field_u3a) %>% 
  remove_NAs(.)
df_u3a_f <- df_u3a %>% 
  filter(a1pkt_type == "F") %>% 
  rename_at(.vars = vars(one_of(u3a_fvp_vars)),
            # .funs = funs(str_replace(., "(.*)", "fu_")))
            .funs = list(~str_replace(., "(.*)", "fu_\\1")))
# _ _ UDS 3 (Archive) TVP ----
u3n_tvp_vars <- str_replace(fields_u3n_raw_tele, "tele_", "")
u3a_tvp_vars <- trans_dict %>% 
  filter(field_u3n %in% u3n_tvp_vars) %>% 
  pull(field_u3a) %>% 
  remove_NAs(.)
df_u3a_t <- df_u3a %>% 
  filter(a1pkt_type == "T") %>% 
  rename_at(.vars = vars(one_of(u3a_tvp_vars)),
            # .funs = funs(str_replace(., "(.*)", "tele_")))
            .funs = list(~str_replace(., "(.*)", "tele_\\1")))
# _ _ Row bind UDS 3 (Archive) I+F+T ----
df_u3a_ift <- bind_rows(df_u3a_i, df_u3a_f, df_u3a_t)
```

# Stitch Data Together

Based on the translation dictionary (`WIP__translation_dictionary.xlsx`), we'll 
stitch together all the UDS data into one harmonized dataset.

## Build Standard Names DF (`std_names_df`)

### Set up the empty df

```{r}
# _ Build standard names df ----
## Set up empty df
std_names_df <- data.frame(matrix(data = NA_character_,
                                  nrow = 0,
                                  ncol = 2),
                           stringsAsFactors = FALSE) %>% 
  as_tibble()
names(std_names_df) <- c("std_source", "std_field")
head(std_names_df) # %>% pretty_print_df()
```

### Loop over rows of `trans_dict` to standardize field names

`trans_dict` is just a df of the spreadsheet `WIP__translation_dictionary.xlsx`.
From this, we'll grab first the UDS 3 New field name; if that doesn't exist,
we'll grab the UDS 3 Archive field name; if that doesn't exist, it'll be the UDS
2 field name.

From this process is born the standard translation dictionary, `trans_dict_std`.

```{r}
## Loop through rows of `trans_dict`
for (i in seq_len(nrow(trans_dict))) {
  
  ## Std field name is from UDS 3 (New), then UDS 3 (Archive), then UDS 2
  if (!is.na(trans_dict[i, "field_u3n"])) {
    std_names_df[i, ] <- list("field_u3n", trans_dict[[i, "field_u3n"]])
  } else if (!is.na(trans_dict[i, "field_u3a"])) {
    std_names_df[i, ] <- list("field_u3a", trans_dict[[i, "field_u3a"]])
  } else if (!is.na(trans_dict[i, "field_u2"])) {
    std_names_df[i, ] <- list("field_u2", trans_dict[[i, "field_u2"]])
  }
  
}
trans_dict_std <- cbind(trans_dict, std_names_df)
trans_dict_std %>% 
  select(-form_u2, -form_u3a, -form_u3n, 
         -Accounted_For, -Flag, -std_field) %>% 
  head() # %>% pretty_print_df()
```

### Append `fu_*` and `tele_*` fields to bottom of Standard Translation Dictionary

This chunk uses data from human-created/-maintained `WIP__uds3_ift_matches.xlsx`
to append `fu_*` and `tele_*` fields to the bottom of the Standard Translation
Dictionary (which started out as human-created/-maintained
`WIP__translation_dictionary.xlsx`).

```{r}
## Append `fu_*` fields ----
u3n_ift_match_f <- u3n_ift_match %>%
  filter(!is.na(field_fvp)) %>%
  filter(field_ivp %in% u3n_fvp_vars) %>%
  pull(field_ivp)
for (i in seq_along(u3n_ift_match_f)) {
  # cat(paste(i, u3n_ift_match_f[i], "\n"))
  # cat(paste(i, nrow(trans_dict_std)+i, "\n"))
  curr_row <- nrow(trans_dict_std) + 1
  ## Add `fu_*` field from within trans_dict_std to end of trans_dict_std
  ## UDS 2
  trans_dict_std[curr_row, "field_u2"] <-
    paste0("fu_",
           trans_dict_std[[
             which(trans_dict_std$field_u3n == u3n_ift_match_f[i]), "field_u2"
             ]])
  # UDS 3 (Archive)
  trans_dict_std[curr_row, "field_u3a"] <-
    paste0("fu_",
           trans_dict_std[[
             which(trans_dict_std$field_u3n == u3n_ift_match_f[i]), "field_u3a"
             ]])
  # UDS 3 (New)
  trans_dict_std[curr_row, "field_u3n"] <-
    paste0("fu_",
           trans_dict_std[[
             which(trans_dict_std$field_u3n == u3n_ift_match_f[i]), "field_u3n"
             ]])
  trans_dict_std[curr_row, "form_u3n"] <-
    str_replace(
      trans_dict_std[[
        which(trans_dict_std$field_u3n == u3n_ift_match_f[i]), "form_u3n"
        ]],
      pattern = "ivp_",
      replacement = "fvp_")
  trans_dict_std[curr_row, "Notes"] <-
    "__ synthetic field in UDS 2, UDS 3 (Archive) __"
  trans_dict_std[curr_row, "std_source"] <- "field_u3n"
  trans_dict_std[curr_row, "std_field"] <-
    trans_dict_std[[curr_row, "field_u3n"]]
}
tail(trans_dict_std) # %>% pretty_print_df()
```

```{r}
## Append `tele_*` fields ----
u3n_ift_match_t <- u3n_ift_match %>%
  filter(!is.na(field_tvp)) %>%
  filter(field_ivp %in% u3n_tvp_vars) %>%
  pull(field_ivp)
for (i in seq_along(u3n_ift_match_t)) {
  # cat(paste(i, u3n_ift_match_t[i], "\n"))
  # cat(paste(i, nrow(trans_dict_std)+i, "\n"))
  curr_row <- nrow(trans_dict_std) + 1
  ## Add `tele_*` field from within trans_dict_std to end of trans_dict_std
  ## UDS 2
  trans_dict_std[curr_row, "field_u2"] <-
    paste0("tele_",
           trans_dict_std[[
             which(trans_dict_std$field_u3n == u3n_ift_match_t[i]), "field_u2"
             ]])
  # UDS 3 (Archive)
  trans_dict_std[curr_row, "field_u3a"] <-
    paste0("tele_",
           trans_dict_std[[
             which(trans_dict_std$field_u3n == u3n_ift_match_t[i]), "field_u3a"
             ]])
  # UDS 3 (New)
  trans_dict_std[curr_row, "field_u3n"] <-
    paste0("tele_",
           trans_dict_std[[
             which(trans_dict_std$field_u3n == u3n_ift_match_t[i]), "field_u3n"
             ]])
  trans_dict_std[curr_row, "form_u3n"] <-
    str_replace(
      trans_dict_std[[
        which(trans_dict_std$field_u3n == u3n_ift_match_t[i]), "form_u3n"
        ]],
      pattern = "ivp_",
      replacement = "tvp_")
  trans_dict_std[curr_row, "Notes"] <-
    "__ synthetic field in UDS 2, UDS 3 (Archive) __"
  trans_dict_std[curr_row, "std_source"] <- "field_u3n"
  trans_dict_std[curr_row, "std_field"] <-
    trans_dict_std[[curr_row, "field_u3n"]]
}
tail(trans_dict_std) # %>% pretty_print_df()
```

Now remove any instances of non-existing field names after `fu_*` and `tele_*` 
preprends.

```{r}
# _ Remove any instances of "fu_NA", "tele_NA", "fu_", "tele_" -----
trans_dict_std <- trans_dict_std %>% na_if("fu_NA")
trans_dict_std <- trans_dict_std %>% na_if("tele_NA")
trans_dict_std <- trans_dict_std %>% na_if("fu_")
trans_dict_std <- trans_dict_std %>% na_if("tele_")
tail(trans_dict_std) # %>% pretty_print_df()
```

Whatever export fields that aren't included in the standardized translation 
dictionary (`trans_dict_std`) need to be included. Otherwise, these fields won't
be included in the integrated dataset.

UDS 2 fields in `export_fields_u2_df` but NOT in `trans_dict`
```{r}
export_fields_data_dict_u2_df <-
  left_join(export_fields_u2_df, 
            data_dict_u2_df[, c("field_name", "form_name")],
            by = c("original_field_name" = "field_name")) %>% 
  mutate(form_name = case_when(
    str_detect(export_field_name, "(?<!not)_complete$") ~ # negative lookbehind
      str_replace(export_field_name, pattern = "(?<!not)_complete$", ""),
    TRUE ~ form_name
  ))
missing_fields_u2_df <- export_fields_data_dict_u2_df %>% 
  filter(!(export_field_name %in% trans_dict_std$field_u2)) %>% 
  select(field_u2 = export_field_name,
         form_u2 = form_name) %>% 
  mutate(std_source = "field_u2",
         std_field = field_u2)
```

UDS 3 Archive fields in `export_fields_u3a_df` but NOT in `trans_dict`
```{r}
export_fields_data_dict_u3a_df <-
  left_join(export_fields_u3a_df, 
            data_dict_u3a_df[, c("field_name", "form_name")],
            by = c("original_field_name" = "field_name")) %>% 
  mutate(form_name = case_when(
    str_detect(export_field_name, "(?<!not)_complete$") ~ # negative lookbehind
      str_replace(export_field_name, pattern = "(?<!not)_complete$", ""),
    TRUE ~ form_name
  ))
missing_fields_u3a_df <- export_fields_data_dict_u3a_df %>% 
  filter(!(export_field_name %in% trans_dict_std$field_u3a)) %>% 
  select(field_u3a = export_field_name,
         form_u3a = form_name) %>% 
  mutate(std_source = "field_u3a",
         std_field = field_u3a)
```

UDS 3 New fields in `export_fields_u3n_df` but NOT in `trans_dict`
```{r}
export_fields_data_dict_u3n_df <-
  left_join(export_fields_u3n_df, 
            data_dict_u3n_df[, c("field_name", "form_name")],
            by = c("original_field_name" = "field_name")) %>% 
  mutate(form_name = case_when(
    str_detect(export_field_name, "(?<!not)_complete$") ~ # negative lookbehind
      str_replace(export_field_name, pattern = "(?<!not)_complete$", ""),
    TRUE ~ form_name
  ))
missing_fields_u3n_df <- export_fields_data_dict_u3n_df %>% 
  filter(!(export_field_name %in% trans_dict_std$field_u3n)) %>% 
  select(field_u3n = export_field_name, 
         form_u3n = form_name) %>% 
  mutate(std_source = "field_u3n",
         std_field = field_u3n)
```

Row-bind missing fields to `trans_dict_std`
```{r}
trans_dict_std <-
  bind_rows(trans_dict_std,
            missing_fields_u2_df,
            missing_fields_u3a_df,
            missing_fields_u3n_df)
```

Group by forms/instruments.
```{r}
trans_dict_std <- trans_dict_std %>%
  mutate(std_form = case_when(
    # header + a1
    form_u3n == "header" |
      form_u3n == "ivp_a1" | form_u3n == "fvp_a1" | form_u3n == "tvp_a1" |
      form_u3a == "registration_form" |
      form_u3a == "form_a1_participant_demographics" |
      form_u2 == "registration_form" |
      form_u2 == "demographic_data" |
      form_u2 == "form_a1_subject_demographics" ~ "header_a1",
    # a2
    form_u3n == "ivp_a2" | form_u3n == "fvp_a2" | form_u3n == "tvp_a2" | 
      form_u3a == "form_a2_informant_demographics" |
      form_u2 == "form_a2_informant_demographics" ~ "a2",
    # a3
    form_u3n == "ivp_a3" | form_u3n == "fvp_a3" | form_u3n == "tvp_a3" | 
      form_u3a == "form_a3_subject_family_history" |
      form_u2 == "form_a3_subject_family_history" ~ "a3",
    # a4
    form_u3n == "ivp_a4" | form_u3n == "fvp_a4" | form_u3n == "tvp_a4" | 
      form_u3a == "form_a4_subject_medications" |
      form_u2 == "form_a4_subject_medications" ~ "a4",
    # a5
    form_u3n == "ivp_a5" | form_u3n == "fvp_a5" | form_u3n == "tvp_a5" | 
      form_u3a == "form_a5_subject_health_history" |
      form_u2 == "form_a5_subject_health_history" ~ "a5",
    # b1
    form_u3n == "ivp_b1" | form_u3n == "fvp_b1" | form_u3n == "tvp_b1" | 
      form_u3a == "form_b1_evaluation_form" |
      form_u2 == "form_b1_evaluation_form" ~ "b1",
    # b2
    form_u2 == "form_b2_evaluation_form_his_and_cvd" ~ "b2",
    # b3
    form_u2 == "form_b3_evaluation_form_updrs_motor_exam" ~ "b3",
    # b4
    form_u3n == "ivp_b4" | form_u3n == "fvp_b4" | form_u3n == "tvp_b4" | 
      form_u3a == "form_b4_cdr" |
      form_u2 == "form_b4_cdr" ~ "b4",
    # b5
    form_u3n == "ivp_b5" | form_u3n == "fvp_b5" | form_u3n == "tvp_b5" | 
      form_u3a == "form_b5_behavioral_assessment_npiq" |
      form_u2 == "form_b5_behavioral_assessment_npi_q" ~ "b5",
    # b6
    form_u3n == "ivp_b6" | form_u3n == "fvp_b6" | form_u3n == "tvp_b6" | 
      form_u3a == "form_b6_gds" |
      form_u2 == "form_b6_gds" ~ "b6",
    # b7
    form_u3n == "ivp_b7" | form_u3n == "fvp_b7" | form_u3n == "tvp_b7" | 
      form_u3a == "form_b7_functional_assessment_faq" |
      form_u2 == "form_b7_functional_assessment_faq" ~ "b7",
    # b8
    form_u3n == "ivp_b8" | form_u3n == "fvp_b8" | form_u3n == "tvp_b8" | 
      form_u3a == "form_b8_physical_neurological_exam_findings" |
      form_u2 == "form_b8_physical_neurological_exam_findings" ~ "b8",
    # b9
    form_u3n == "ivp_b9" | form_u3n == "fvp_b9" | form_u3n == "tvp_b9" | 
      form_u3a == "form_b9_clinician_judgment_of_symptoms" |
      form_u2 == "form_b9_clinician_judgment_of_symptoms" ~ "b9",
    # c1c2
    form_u3n == "ivp_c2" | form_u3n == "fvp_c2" | form_u3n == "tvp_c2" | 
      form_u3n == "fvp_c1" |
      form_u3n == "form_c1_c2_mmse_and_npsych" |
      form_u3a == "form_c1_c2_mmse_and_npsych" |
      form_u2 == "form_c1_mmse_and_npsych" ~ "c1c2",
    # d1
    form_u3n == "ivp_d1" | form_u3n == "fvp_d1" | form_u3n == "tvp_d1" | 
      form_u3a == "form_d1_clinician_diagnosis" |
      form_u2 == "form_d1_clinician_diagnosis" ~ "d1",
    # d2
    form_u3n == "ivp_d2" | form_u3n == "fvp_d2" | form_u3n == "tvp_d2" | 
      form_u3a == "form_d2_clinician_diagnosis" ~ "d2",
    # e1
    form_u2 == "form_e1_imaging_labs" ~ "e1",
    # z1
    form_u3n == "ivp_z1" | form_u3n == "fvp_z1" | form_u3n == "tvp_z1" | 
      form_u3a == "form_z1_checklist" |
      form_u2 == "form_z1_checklist" ~ "z1",
    # m1
    form_u3n == "m1" |
      form_u3a == "form_milestones" |
      form_u2 == "form_milestones" ~ "m1",
    # caregiver
    form_u3n == "caregiver_questionnaire" |
      form_u3a == "caregiver_questionnaire" |
      form_u2 == "caregiver_questionnaire" ~ "caregiver",
    # macq
    form_u3n == "mac_q" |
      form_u3a == "macq_patient"  ~ "macq",
    # adco
    form_u3n == "adco" |
      form_u3a == "adco" |
      form_u2 == "adco" ~ "adco",
    # lsns6
    form_u3n == "lsns6" |
      form_u3a == "lsns6" |
      form_u2 == "lsns6" ~ "lsns6",
    # stroop
    form_u3a == "stroop" |
      form_u2 == "stroop" ~ "stroop",
    # wrat3
    form_u3a == "wrat_3" |
      form_u2 == "wrat_3" ~ "wrat3",
    # toolbox
    form_u3n == "tool_box" |
      form_u3a == "tool_box" |
      form_u2 == "tool_box" ~ "toolbox",
    # cogstate
    form_u3n == "cogstate" |
      form_u3a == "cogstate" |
      form_u2 == "cogstate" ~ "cogstate",
    # ipad_toolbox
    form_u3n == "ipad_tool_box" ~ "ipad_toolbox",
    # t1
    form_u2 == "form_t1_inclusion" |
      form_u3n == "tvp_t1" ~ "t1",
    # ftld_initial_packet_v9
    form_u3a == "ftld_initial_packet_v9" ~ "ftld_initial_packet_v9",
    # ftld_a3a
    form_u3n == "ftld_a3a" ~ "ftld_a3a",
    # ftld_b3f
    form_u3n == "ftld_b3f" ~ "ftld_b3f",
    # ftld_b9f
    form_u3n == "ftld_b9f" ~ "ftld_b9f",
    # ftld_c1f
    form_u3n == "ftld_c1f" ~ "ftld_c1f",
    # ftld_c2f
    form_u3n == "ftld_c2f" ~ "ftld_c2f",
    # ftld_c3f
    form_u3n == "ftld_c3f" ~ "ftld_c3f",
    # ftld_c4f
    form_u3n == "ftld_c4f" ~ "ftld_c4f",
    # ftld_c5f
    form_u3n == "ftld_c5f" ~ "ftld_c5f",
    # ftld_c6f
    form_u3n == "ftld_c6f" ~ "ftld_c6f",
    # ftld_e2f
    form_u3n == "ftld_e2f" ~ "ftld_e2f",
    # ftld_e3f
    form_u3n == "ftld_e3f" ~ "ftld_e3f",
    # ftld_z1f
    form_u3n == "ftld_z1f" ~ "ftld_z1f",
    # jolo
    form_u3n == "jolo" ~ "jolo",
    # hvlt
    form_u3n == "hvlt" ~ "hvlt",
    # emory_wcst
    form_u3n == "emory_wcst" ~ "emory_wcst",
    # wtar
    form_u3n == "wtar" ~ "wtar",
    # cowa_cfl
    form_u3n == "cowa_cfl" ~ "cowa_cfl",
    # fdmse
    form_u3n == "financial_decision_making_self_efficacy_form" ~ "fdmse",
    # lfdss
    form_u3n == "lfdss_for_professionals" ~ "lfdss",
    # oltt
    form_u3n == "oltt" ~ "oltt",
    # hol
    form_u3n == "hol_questionnaire" ~ "hol",
    # behav_obs
    form_u3n == "behavioral_observations" ~ "behav_obs",
    # b1l
    form_u3n == "ivp_b1l" ~ "b1l",
    # b2l
    form_u3n == "ivp_b2l" ~ "b2l",
    # b3l
    form_u3n == "b3l" ~ "b3l",
    # b4l
    form_u3n == "ivp_b4l" ~ "b4l",
    # b5l
    form_u3n == "iv_b5l" ~ "b5l",
    # b6l
    form_u3n == "iv_b6l" ~ "b6l",
    # b7l
    form_u3n == "ivp_bl7" ~ "b7l",
    # b8l
    form_u3n == "iv_bl8" ~ "b8l",
    # b9l
    form_u3n == "iv_b9l" ~ "b9l",
    # c1l
    form_u3n == "c1l" ~ "c1l",
    # d1l
    form_u3n == "d1l" ~ "d1l",
    # e1l
    form_u3n == "ivp_e1l" ~ "e1l",
    # e2l
    form_u3n == "ivp_e2l" ~ "e2l",
    # e3l
    form_u3n == "ivp_e3l" ~ "e3l",
    # ffi
    form_u3n == "family_friends_interview_ffi" ~ "ffi"
  ))
```

Write `trans_dict_std` to file.
```{r}
readr::write_csv(trans_dict_std, "STD__translation_dictionary.csv", na = "")
```


## Build Stitched DF (`df_u2_u3a_u3n`)

### Create empty df

```{r}
# _ Build stitched data df ----
## Stitched df is `df_u2_u3a_u3n`
df_u2_u3a_u3n <- data.frame(matrix(data = NA_character_,
                                   nrow = sum(nrow(df_u2_ift),
                                              nrow(df_u3a_ift),
                                              nrow(df_u3n)),
                                   ncol = nrow(trans_dict_std))) %>% 
  as_tibble()
names(df_u2_u3a_u3n) <- trans_dict_std$std_field
```

### Build `df_u2_u3a_u3n`

To accomplish this, we iterate over the rows of `trans_dict_std` and build 
`df_u2_u3a_u3n` column by column.

```{r}
# Loop through `trans_dict_std` rows to build stitched df column by column
## ... using df_u2_ift, df_u3a_ift, df_u3n
cat("Number of columns in df_u2_u3a_u3n df:\n")
for (i in seq_len(nrow(trans_dict_std))) {
  # for (i in 1:601) {
  cat(paste0(i, " "))
  
  ## Build temp UDS 2 vector
  if (!is.na(trans_dict_std[i, "field_u2"]) &&
      !is.null(df_u2_ift[[trans_dict_std[i, "field_u2"]]])) {
    temp_u2_vec <- df_u2_ift[[trans_dict_std[i, "field_u2"]]]
  } else {
    temp_u2_vec <- rep(NA_character_, times = nrow(df_u2_ift))
  }
  
  ## Build temp UDS 3 (Archive) vector
  if (!is.na(trans_dict_std[i, "field_u3a"]) &&
      !is.null(df_u3a_ift[[trans_dict_std[i, "field_u3a"]]])) {
    temp_u3a_vec <- df_u3a_ift[[trans_dict_std[i, "field_u3a"]]]
  } else {
    temp_u3a_vec <- rep(NA_character_, times = nrow(df_u3a_ift))
  }
  
  ## Build temp UDS 3 (New) vector
  if (!is.na(trans_dict_std[i, "field_u3n"]) &&
      !is.null(df_u3n[[trans_dict_std[i, "field_u3n"]]])) {
    temp_u3n_vec <- df_u3n[[trans_dict_std[i, "field_u3n"]]]
  } else {
    temp_u3n_vec <- rep(NA_character_, times = nrow(df_u3n))
  }
  
  ## Concat `temp_*_vec` vectors
  temp_u2_u3a_u3n_vec <- c(temp_u2_vec, temp_u3a_vec, temp_u3n_vec)
  # print(length(temp_u2_u3a_u3n_vec))
  
  ## Lay concat'd `temp_*_vec` vectors into stitched df column
  df_u2_u3a_u3n[, i] <- temp_u2_u3a_u3n_vec
}
```

Convert any date strings like _*MM/DD/YYYY*_ to _*YYYY-MM-DD*_.

```{r}
df_u2_u3a_u3n <- df_u2_u3a_u3n %>% 
  purrr::map_df(~ str_replace(.x,
                              "^(\\d{1})/(\\d{1})/(\\d{4})$",
                              "\\3-0\\1-0\\2")) %>% 
  purrr::map_df(~ str_replace(.x,
                              "^(\\d{1})/(\\d{2})/(\\d{4})$",
                              "\\3-0\\1-\\2")) %>% 
  purrr::map_df(~ str_replace(.x,
                              "^(\\d{2})/(\\d{1})/(\\d{4})$",
                              "\\3-\\1-0\\2")) %>%
  purrr::map_df(~ str_replace(.x,
                              "^(\\d{2})/(\\d{2})/(\\d{4})$",
                              "\\3-\\1-\\2"))
```


### Reduce the size of `df_u2_u3a_u3n` by guessing column data types

```{r}
print(object.size(df_u2_u3a_u3n), units = "auto")
# _ Guess column types
df_u2_u3a_u3n <- suppressMessages( readr::type_convert(df_u2_u3a_u3n) )
print(object.size(df_u2_u3a_u3n), units = "auto")
```

## Write Harmonized Data To File

Write the resulting harmonized dataset `df_u2_u3a_u3n` to a CSV and RDS files of
the same name.

(First check that there's a dated directory in place.)

```{r}
system(paste0("if [[ ! -d \"./MDI Data/", Sys.Date(), "\" ]]; then mkdir \"./MDI Data/", Sys.Date(), "\" ; fi;"))
```

```{r}
# WRITE TO CSV ----
readr::write_csv(df_u2_u3a_u3n, 
                 paste0("MDI Data/", Sys.Date(), "/df_u2_u3a_u3n.csv"), 
                 na = "")
```

```{r}
# WRITE TO RDS ---
saveRDS(df_u2_u3a_u3n, 
        paste0("MDI Data/", Sys.Date(), "/df_u2_u3a_u3n.Rds"))
```


# Parse Stitched Data by "Standard" Form

```{r}
std_forms <- 
  trans_dict_std %>% 
  distinct(std_form) %>% 
  pull() %>% 
  stringi::stri_remove_empty_na()

ls_dfs_u2_u3a_u3n <- list()

for (sd in std_forms) {
  cat(paste0("Processing ", sd, "...\n"))
  
  fields_primkey <- c("ptid", "form_date")
  fields_rlvnt <-
    trans_dict_std %>% 
    filter(std_form == sd) %>% 
    pull(std_field)
  fields_tmp <- c(fields_primkey, fields_rlvnt) %>% unique()
  
  ls_dfs_u2_u3a_u3n[[sd]] <- 
    df_u2_u3a_u3n %>% 
    select(all_of(fields_tmp)) %>% 
    get_nonempty_records(relevant_fields = fields_rlvnt) %>%
    # get_nonempty_fields() %>% # saves space but better to have every field
    type_convert(col_types = cols(.default = col_guess()))
  
  # Find columns that are guessed as integers
  # (readr::type_convert() above doesn't coerce to integers)
  col_types <- 
    purrr::map(ls_dfs_u2_u3a_u3n[[sd]], guess_parser, guess_integer = TRUE)
  
  ls_dfs_u2_u3a_u3n[[sd]] <-
    purrr::imap_dfc(.x = col_types,
                    .f = function(.x, .y) {
                      
                      # .x is col_type value
                      # .y is col_type name
                      
                      if (.x == "integer") {
                        ls_dfs_u2_u3a_u3n[[sd]][[.y]] <- 
                          ls_dfs_u2_u3a_u3n[[sd]][[.y]] %>% as.integer()
                      } else {
                        ls_dfs_u2_u3a_u3n[[sd]][[.y]] <-
                          ls_dfs_u2_u3a_u3n[[sd]][[.y]]
                      }
                      
                    })
}
```

## Write `ls_dfs_u2_u3a_u3n` to File

```{r}
saveRDS(ls_dfs_u2_u3a_u3n, 
        paste0("MDI Data/", Sys.Date(), "/ls_dfs_u2_u3a_u3n.Rds"))
```


# Build Data Dictionary

## Get UDS Fields

### UDS 2
```{r}
# UDS 2
data_dict_fields_u2_raw <- trans_dict_std %>% 
  select(std_source, std_field) %>% 
  filter(std_source == "field_u2") %>% 
  pull(std_field)
```

### UDS 3 Archive
```{r}
# UDS 3 (Archive)
data_dict_fields_u3a_raw <- trans_dict_std %>% 
  select(std_source, std_field) %>% 
  filter(std_source == "field_u3a") %>% 
  pull(std_field)
```

### UDS 3 New
```{r}
# UDS 3 (New)
data_dict_fields_u3n_raw <- trans_dict_std %>% 
  select(std_source, std_field) %>% 
  filter(std_source == "field_u3n") %>% 
  pull(std_field)
```

## Retrieve Data Dictionary via REDCap API

### UDS 2
```{r}
if (GET_API_DATA) {
  json_data_dict_u2 <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS2,
    content="metadata",
    format="json",
    returnFormat="json",
    .opts = list(ssl.verifypeer = TRUE) # using linux
  ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
df_data_dict_u2_all <- jsonlite::fromJSON(json_data_dict_u2)
df_data_dict_u2 <- df_data_dict_u2_all %>% 
  filter(field_name %in% data_dict_fields_u2_raw)
```

### UDS 3 (Archive)
```{r}
if (GET_API_DATA) {
  json_data_dict_u3a <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS3a,
    content="metadata",
    format="json",
    returnFormat="json",
    .opts = list(ssl.verifypeer = TRUE) # using linux
  ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
df_data_dict_u3a_all <- jsonlite::fromJSON(json_data_dict_u3a)
df_data_dict_u3a <- df_data_dict_u3a_all %>% 
  filter(field_name %in% data_dict_fields_u3a_raw)
```

### UDS 3 (New)
```{r}
if (GET_API_DATA) {
  json_data_dict_u3n <- RCurl::postForm(
    uri=REDCAP_API_URI,
    token=REDCAP_API_TOKEN_UDS3n,
    content="metadata",
    format="json",
    returnFormat="json",
    .opts = list(ssl.verifypeer = TRUE) # using linux
  ) %>% 
    str_replace_all(pattern = "\r\n|\r|\n|\t", replacement = " ")
}
df_data_dict_u3n_all <- jsonlite::fromJSON(json_data_dict_u3n)
df_data_dict_u3n <- df_data_dict_u3n_all %>% 
  filter(field_name %in% data_dict_fields_u3n_raw)
```

## Rowbind Data Dictionaries & Order

Order by form name, then field name.

```{r}
df_data_dict <- bind_rows(df_data_dict_u2,
                          df_data_dict_u3a,
                          df_data_dict_u3n)
df_data_dict_form <- df_data_dict %>% 
  arrange(form_name, field_name)
# df_data_dict_field <- df_data_dict %>% 
#   arrange(field_name)

head(df_data_dict_form) %>% 
  select(field_name, form_name, section_header, field_type, field_label,
         select_choices_or_calculations, field_note) # %>% pretty_print_df()

# head(df_data_dict_field) # %>% pretty_print_df()
```

## Write Harmonized Unified Data Dictionary To CSV

```{r}
readr::write_csv(df_data_dict_form, "df_data_dict_form.csv", na = "")
# readr::write_csv(df_data_dict_field, "df_data_dict_field.csv", na = "")
```


```{r echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
